---
title: "Week 4 Assignment"
author: "Rahul Jain"
date: "16/04/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is the reproducible pitch presentation for Week 4 assignment for Course - Developing Data Products. In this 
presentation, I will present the details of the model implemented on shiny app : 

https://rjain92.shinyapps.io/Basic_Model/

Github repo for this project - https://github.com/jnrahul92/cs_data_products/tree/master/Week_4

## Swiss Dataset {.smaller}

First, let me show you the dataset that I have used for creating the shiny app

```{r echo=TRUE,warning=FALSE}
data("swiss")
summary(swiss)
```

## Model Creation for Predicting Fertility {.smaller}

```{r echo=TRUE,warning=FALSE}
fit <- lm(Fertility~Education,data = swiss)
summary(fit)
```

Model fit summary shows that Education is a highly significant variable in the linear model. Also, we can see that adjusted r-squared is around 0.43. We can add 
further parameters to the model to create a better model

## Predicion using the simple linear model {.smaller}


```{r echo=TRUE,warning=FALSE,fig.width=6,fig.height=4}
prediction <- predict(fit, newdata = data.frame(Education = 25))
plot(swiss$Examination,swiss$Fertility, xlab = "Education Level",
             ylab = "Fertility", main = "Education Level vs Fertility")
abline(fit,col="red",lwd=2)
abline(h=prediction,col="blue")
abline(v=25,col = "blue")
```